```{r echo=FALSE}

##########
# Author: Qingfei Pan (Qingfei.Pan<@>hotmail.com), SJCRH, USA
# Version: 2.0 (Jan. 2, 2019)
# This version fixed the bug caused by the gene list of no MT-/mt-.
#
# NOTE: This script is used for Quality Control analysis for the samples with CellRanger reports. This script will automatically search the 'metrics_summary.csv' file generated by CellRanger. Please make sure this file could be found in the default folder, or please manually input the directory of this file in codes.
##########

# Read the arguments
##argv <- commandArgs(TRUE)
sample <- argv[1]
reference <- argv[2]
indir <- argv[3]
outdir <- argv[4]
```

```{r setup, include=FALSE}
library(Seurat)
library(dplyr)
library(Matrix)
library(ggplot2)
library(condformat)
library(knitr)
library(kableExtra)
```

```{r echo = FALSE}
## Input: Read the 10X scRNA-Seq data
data <- Read10X(data.dir = indir)

## Output: Set the directory
knitr::opts_knit$set(root.dir = outdir)
```

## Sample information

```{r echo=FALSE}
# Count the genes identified in >=1 cell(s)
cells_per_gene <- data.frame(ncells = rowSums(sign(data)))
preqc_genes <- sum(cells_per_gene$ncells > 0)

# Count the cells with >=1 identified gene(s)
genes_per_cell <- data.frame(ngenes = colSums(sign(data)))
preqc_cells <- sum(genes_per_cell$ngenes > 0)

sample_info_c1 <- c("Sample ID", "Reference", "Input Directory", "Output Directory", "Raw Genes", "Raw Cells")
sample_info_c2 <- c(sample, reference, indir, outdir, preqc_genes, preqc_cells)
sample_info <- matrix(c(sample_info_c1, sample_info_c2), ncol = 2, byrow = F)
sample_info %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(1, bold = T) %>% column_spec(2, color = "red", bold = T)
```

## 1 Quality control on genes
### 1.1 Evaluate the quality of genes
```{r echo = FALSE}
# Visulize the distribution of cell counts of each gene
nCell_detected <- data.frame(ncells = rowSums(sign(data)))
ggplot(data = nCell_detected, aes(log10(nCell_detected$ncells + 1))) + geom_histogram(bins = 100) + labs(x = "LOG10 (Cell counts + 1)", y = "Gene counts", title = "Distribution of Cell Counts among Genes") + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 12, face = "bold"), title = element_text(size = 14, face = "bold"))
ggsave(filename = "1_1_distribution_of_cell_counts_among_genes.pdf", scale = 1, width = 10, height = 10, units = "in", dpi = 300)
```

### 1.2 Remove the low-quality genes
```{r echo = FALSE}
percent.nCell_cutoff <- 0.01 ## Genes expressed in less cells than this percentage will be removed. Manually adjust it accordingly.
nCell_cutoff <- floor(percent.nCell_cutoff * preqc_cells)
nCell_total <- preqc_genes; nCell_clean <- sum(nCell_detected >= nCell_cutoff); nCell_remove <- (nCell_total - nCell_clean);
per.nCell_remove <- paste((round((nCell_remove / nCell_total * 100), 2)), "%")
per.nCell_clean <- paste((round((nCell_clean / nCell_total * 100), 2)), "%")
gene_table_c1 <- c(nCell_total, nCell_remove, nCell_clean)
gene_table_c2 <- c("100%", per.nCell_remove, per.nCell_clean)
gene_table <- matrix(c(gene_table_c1, gene_table_c2), ncol = 2, byrow = F)
rownames(gene_table) <- c("Gene Total", "Gene Removed", "Gene Remained")
colnames(gene_table) <- c("Number", "Percent")
gene_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(2:3, bold = T, color = "Red") %>% add_footnote(paste0("Genes expressed in less than ", (100 * percent.nCell_cutoff), "% (", nCell_cutoff, ") cells were removed."),  notation = "number")
```

## 2 Quality control on cells

```{r echo = FALSE}
# Setup the Seurat Object
Obj <- CreateSeuratObject(raw.data = data, min.cells = nCell_cutoff, min.genes = 1, project = sample)
```

### 2.1 Evaluate the qulity of cells
```{r echo = FALSE}
# Count mitochondrial genes
mito.genes <- grep(pattern = "mt-|MT-", x = rownames(x = Obj@raw.data), value = TRUE)
percent.mito <- Matrix::colSums(Obj@raw.data[mito.genes, ]) / Matrix::colSums(Obj@raw.data); percent.mito[is.na(percent.mito)] <- 1; ## NAs may cause errors in Mito-related visulization and filtration.
Obj <- AddMetaData(object = Obj, metadata = percent.mito, col.name = "percent.Mito")

# Visulize the distribution of Identified Genes, UMIs and %Mitochondrial genes among cells
VlnPlot(object = Obj, features.plot = c("nGene", "nUMI", "percent.Mito"), nCol = 3, point.size.use = 0, size.x.use = 0, size.title.use = 14) + ggtitle("Distribution of Identified Genes, UMIs and % Mitochondrial Genes among Cells")
ggsave(filename = "2_1_distribution_of_identified_genes_UMIs_percentMito_among_cells.pdf", scale = 1, width = 10, height = 10, units = "in", dpi = 300)

ggplot(data = Obj@meta.data, aes(nGene)) + geom_histogram(bins = 100) + labs(x = "# Identified Genes in Each Cell", y = "Cell Counts", title = "Distribution of Identified Genes among Cells") + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 12, face = "bold"), title = element_text(size = 14, face = "bold"))
ggsave(filename = "2_2_distribution_of_identified_genes_among_cells.pdf", scale = 1, width = 10, height = 10, units = "in", dpi = 300)

ggplot(data = Obj@meta.data, aes(nUMI)) + geom_histogram(bins = 100)  + labs(x = "# Identified UMIs in Each Cell", y = "Cell Counts", title = "Distribution of Identified UMIs among Cells") + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 12, face = "bold"), title = element_text(size = 14, face = "bold"))
ggsave(filename = "2_3_distribution_of_identified_UMIs_among_cells.pdf", scale = 1, width = 10, height = 10, units = "in", dpi = 300)

ggplot(data = Obj@meta.data, aes(percent.mito)) + geom_histogram(bins = 100) + labs(x = "% Mitochondrial Genes in Each Cell", y = "Cell Counts", title = "Distribution of % Mitochondrial Genes among Cells") + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 12, face = "bold"), title = element_text(size = 14, face = "bold"))
ggsave(filename = "2_4_distribution_of_percentMito_among_cells.pdf", scale = 1, width = 10, height = 10, units = "in", dpi = 300)

par(mfrow = c(1, 2))
GenePlot(object = Obj, gene1 = "nUMI", gene2 = "nGene", cex.use = 0.5)
GenePlot(object = Obj, gene1 = "nUMI", gene2 = "percent.Mito", cex.use = 0.5)
hide_info <- dev.copy2pdf(file = "2_5_correlation_gene_percentMito_vs_UMI.pdf", width = 10, height = 10)
hide_info <- dev.off()
```

### 2.2 Evaluate the default cutoffs
#### 2.2.1 Cells removed by poor gene identification
```{r echo = FALSE}
nGene_detected <- Obj@meta.data$nGene; nGene_total <- length(nGene_detected);
nGene_cutoff <- floor(exp(median(log(nGene_detected)) - 3 * mad(log(nGene_detected)))); nGene_clean <- sum(nGene_detected > nGene_cutoff);
nGene_remove = (nGene_total - nGene_clean)
per.nGene_remove = paste((round((nGene_remove / nGene_total*100), 2)), "%")
per.nGene_clean = paste((round((nGene_clean / nGene_total * 100), 2)), "%")
nGene_table_c1 <- c(nGene_total, nGene_remove, nGene_clean)
nGene_table_c2 <- c("100%", per.nGene_remove, per.nGene_clean)
nGene_table <- matrix(c(nGene_table_c1, nGene_table_c2), ncol = 2, byrow = F)
rownames(nGene_table) <- c("Cell Total", "Cell Removed", "Cell Remained")
colnames(nGene_table) <- c("Number", "Percent")
nGene_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(2:3, bold = T, color = "Red") %>% add_footnote(paste0("Cells with less than ", (nGene_cutoff), " (", "Defined by MEDIAN - 3*MAD", ") identified genes were removed."),  notation = "number")
```

#### 2.2.2 Cells removed by poor UMI identification
```{r echo=FALSE}
nUMI_detected <- Obj@meta.data$nUMI; nUMI_total <- length(nUMI_detected);
nUMI_cutoff <- floor(exp(median(log(nUMI_detected)) - 3 * mad(log(nUMI_detected)))); nUMI_clean <- sum(nUMI_detected>nUMI_cutoff);
nUMI_remove = (nUMI_total - nUMI_clean)
per.nUMI_remove = paste((round((nUMI_remove / nUMI_total * 100), 2)), "%")
per.nUMI_clean = paste((round((nUMI_clean / nUMI_total * 100), 2)), "%")
nUMI_table_c1 <- c(nUMI_total, nUMI_remove, nUMI_clean)
nUMI_table_c2 <- c("100%", per.nUMI_remove, per.nUMI_clean)
nUMI_table <- matrix(c(nUMI_table_c1, nUMI_table_c2), ncol = 2, byrow = F)
rownames(nUMI_table) <- c("Cell Total", "Cell Removed", "Cell Remained")
colnames(nUMI_table) <- c("Number", "Percent")
nUMI_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(2:3, bold = T, color = "Red") %>% add_footnote(paste0("Cells with less than ", (nUMI_cutoff), " (", "Defined by MEDIAN - 3*MAD", ") identified UMIs were removed."),  notation = "number")
```

#### 2.2.3 Cells removed by high mitochondrial genes
```{r echo=FALSE}
percent.mito_detected <- Obj@meta.data$percent.Mito; percent.mito_total <- length(percent.mito_detected);
percent.mito_cutoff <- round((median(percent.mito_detected) + 3 * mad(percent.mito_detected)), 4); percent.mito_clean <- sum(percent.mito_detected < percent.mito_cutoff);
percent.mito_remove = (percent.mito_total - percent.mito_clean)
per.percent.mito_remove = paste((round((percent.mito_remove / percent.mito_total * 100), 2)), "%")
per.percent.mito_clean = paste((round((percent.mito_clean / percent.mito_total * 100), 2)), "%")
percent.mito_table_c1 <- c(percent.mito_total, percent.mito_remove, percent.mito_clean)
percent.mito_table_c2 <- c("100%", per.percent.mito_remove, per.percent.mito_clean)
percent.mito_table <- matrix(c(percent.mito_table_c1, percent.mito_table_c2), ncol = 2, byrow = F)
rownames(percent.mito_table) <- c("Cell Total", "Cell Removed", "Cell Remained")
colnames(percent.mito_table) <- c("Number", "Percent")
percent.mito_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(2:3, bold = T, color = "Red") %>% add_footnote(paste0("Cells with over than ", (percent.mito_cutoff), " (", "Defined by MEDIAN + 3*MAD", ") mitochondrial genes were removed."),  notation = "number")
```

### 2.3 Remove the low-quality cells
```{r echo = FALSE}
manual_cutoffs <- 0 ## "0" for default method, and "1" for manual cutoffs.
cutoffs_low <- c(nGene_cutoff, nUMI_cutoff, -Inf); cutoffs_high <- c(Inf, Inf, percent.mito_cutoff); ## Manually adjust them accordingly.
cutoffs_low[1] <- max(nGene_cutoff, 50); cutoffs_low[2] <- max(nUMI_cutoff, 100); cutoffs_high[3] <- if (percent.mito_cutoff <= 0) 0.8 else (min(percent.mito_cutoff, 0.8)); ## Fix the bug caused by gene list with no MT-/mt-.
Obj <- FilterCells(object = Obj, subset.names = c("nGene", "nUMI", "percent.Mito"), low.thresholds = cutoffs_low, high.thresholds = cutoffs_high)

para_table_r1 <- c(nCell_cutoff, cutoffs_low[1], cutoffs_low[2], paste0((cutoffs_low[3] * 100), "%"))
para_table_r2 <- c(Inf, cutoffs_high[1], cutoffs_high[2], paste0((cutoffs_high[3] * 100), "%"))
para_table <- matrix(c(para_table_r1, para_table_r2), ncol = 4, byrow = T)
colnames(para_table) <- c("# Cells per Gene", "# Identified Genes", "# Identified UMIs", "% Mitochondrial Genes")
rownames(para_table) <- c("Low Thresholds", "High Thresholds")
para_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% column_spec(1, bold = T)

result_table <- matrix(c(dim(Obj@data)[1], dim(Obj@data)[2]), ncol = 2, byrow = T)
colnames(result_table) <- c("Qualified Genes", "Qualified Cells")
result_table %>% kable("html", align = "c") %>% kable_styling(bootstrap_options = "striped", font_size = 20) %>% row_spec(1, bold = T, color = "red",background = "lightgreen")

summary_table_r1 = c(round(summary(Obj@meta.data$nGene)[4], 0), summary(Obj@meta.data$nGene)[1], summary(Obj@meta.data$nGene)[2], summary(Obj@meta.data$nGene)[3], summary(Obj@meta.data$nGene)[5], summary(Obj@meta.data$nGene)[6])
summary_table_r2 = c(round(summary(Obj@meta.data$nUMI)[4], 0), summary(Obj@meta.data$nUMI)[1], summary(Obj@meta.data$nUMI)[2], summary(Obj@meta.data$nUMI)[3], summary(Obj@meta.data$nUMI)[5], summary(Obj@meta.data$nUMI)[6])
summary_table <- matrix(c(summary_table_r1, summary_table_r2), ncol = 6, byrow = T)
colnames(summary_table) <- c("Mean", "Min.", "1stQu.", "Median", "3rdQu.", "Max.")
rownames(summary_table) <- c("Identified Genes", "Identified UMIs")
summary_table %>% kable("html", align = "c") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% row_spec(1:2, bold = T, color = "red")

postqc_genes <- dim(Obj@data)[1]; postqc_cells <- dim(Obj@data)[2];
genes_per_cell_median <- (summary(Obj@meta.data$nGene))[3]; genes_per_cell_mean <- floor((summary(Obj@meta.data$nGene))[4]);
umis_per_cell_median <- (summary(Obj@meta.data$nUMI))[3]; umis_per_cell_mean <- floor((summary(Obj@meta.data$nUMI))[4]);
```

## 3 Summary
### 3.1 Key Features
```{r echo=FALSE}
key_c1 <- c("Qualified Cells", "Qualified Genes", "Median Genes per Cell", "Mean UMIs per Cell")
key_c2 <- c(postqc_cells, postqc_genes, genes_per_cell_median, umis_per_cell_mean)
key_table <- matrix(c(key_c1, key_c2), ncol = 2, byrow = F)
t(key_table) %>% kable("html", align = "c") %>% kable_styling(bootstrap_options = "striped", font_size = 20) %>% column_spec(1:4, bold = T) %>% row_spec(2, color = "red", background = "lightgreen")
```

### 3.2 Sample Information
```{r echo=FALSE}
sample_c1 <- c("Name", "Reference", "Chemistry", "Cell Ranger Version", "Input Directory", "Output Directory")
sample_c2 <- c(sample, reference, "Single Cell 3' v2", "2.0.1", indir, outdir)
sample_table <- matrix(c(sample_c1, sample_c2), ncol = 2, byrow = F)
sample_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14)
```

### 3.3 Cell Ranger Report on Sequencing
```{r echo=FALSE,warning=FALSE}
metrics <- read.csv(paste0(indir, "/../../metrics_summary.csv"), header = T, colClasses = "character") ## Please make sure the 'metrics_summary.csv' could be found in the default directory.
sequencing_c1 <- c("Number of Reads", "Valid Barcodes", "Reads Mapped Confidently to Transcriptome", "Reads Mapped Confidently to Exonic Regions", "Reads Mapped Confidently to Intronic Regions", "Reads Mapped Confidently to Intergenic Regions", "Reads Mapped Antisense to Gene", "Sequencing Saturation", "Q30 Bases in Barcode", "Q30 Bases in RNA Read", "Q30 Bases in Sample Index", "Q30 Bases in UMI")
if ("Number.of.Reads" %in% colnames(metrics)) nor <- metrics[1, "Number.of.Reads"] else nor <- "NA"
if ("Valid.Barcodes" %in% colnames(metrics)) vb <- metrics[1, "Valid.Barcodes"] else vb <- "NA"
if ("Reads.Mapped.Confidently.to.Transcriptome" %in% colnames(metrics)){rmctt <- metrics[1, "Reads.Mapped.Confidently.to.Transcriptome"]} else {tag1 <- paste0(reference, ".", "Reads.Mapped.Confidently.to.Transcriptome"); if (tag1 %in% colnames(metrics)){rmctt <- metrics[1, tag1]} else {rmctt <- "NA"}}
if ("Reads.Mapped.Confidently.to.Exonic.Regions" %in% colnames(metrics)){rmcter <- metrics[1, "Reads.Mapped.Confidently.to.Exonic.Regions"]} else {tag2 <- paste0(reference, ".", "Reads.Mapped.Confidently.to.Exonic.Regions"); if (tag2 %in% colnames(metrics)){rmcter <- metrics[1,tag2]} else {rmcter <- "NA"}}
if ("Reads.Mapped.Confidently.to.Intronic.Regions" %in% colnames(metrics)){rmctir <- metrics[1, "Reads.Mapped.Confidently.to.Intronic.Regions"]} else {tag3 <- paste0(reference, ".", "Reads.Mapped.Confidently.to.Intronic.Regions"); if (tag3 %in% colnames(metrics)){rmctir <- metrics[1,tag3]} else {rmctir <- "NA"}}
if ("Reads.Mapped.Confidently.to.Intergenic.Regions" %in% colnames(metrics)){rmctir2 <- metrics[1, "Reads.Mapped.Confidently.to.Intergenic.Regions"]} else {tag4 <- paste0(reference, ".", "Reads.Mapped.Confidently.to.Intergenic.Regions"); if (tag1 %in% colnames(metrics)){rmctir2 <- metrics[1,tag4]} else {rmctir2 <- "NA"}}
if ("Reads.Mapped.Antisense.to.Gene" %in% colnames(metrics)) rmatg <- metrics[1, "Reads.Mapped.Antisense.to.Gene"] else rmatg <- "NA"
if ("Sequencing.Saturation" %in% colnames(metrics)) ss <- metrics[1, "Sequencing.Saturation"] else ss <- "NA"
if ("Q30.Bases.in.Barcode" %in% colnames(metrics)) q30bib <- metrics[1, "Q30.Bases.in.Barcode"] else q30bib <- "NA"
if ("Q30.Bases.in.RNA.Read" %in% colnames(metrics)) q30birr <- metrics[1, "Q30.Bases.in.RNA.Read"] else q30birr <- "NA"
if ("Q30.Bases.in.Sample.Index" %in% colnames(metrics)) q30bisi <- metrics[1, "Q30.Bases.in.Sample.Index"] else q30bisi <- "NA"
if ("Q30.Bases.in.UMI" %in% colnames(metrics)) q30biu <- metrics[1, "Q30.Bases.in.UMI"] else q30biu <- "NA"
sequencing_c2 <- c(as.numeric(gsub(",", "", nor)), vb, rmctt, rmcter, rmctir, rmctir2, rmatg, ss, q30bib, q30birr, q30bisi, q30biu)
sequencing_table <- matrix(c(sequencing_c1, sequencing_c2), ncol = 2, byrow = F)
sequencing_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14)
```

### 3.4 Cell Ranger Report on GEM Partitions
```{r echo=FALSE,warning=FALSE}
gem_c1 <- c("GEMs with >0 Cells", "GEMs with >1 Cell", "Fraction GEMs with >1 Cell", "Fraction GEMs with >1 Cell (Lower Bound)", "Fraction GEMs with >1 Cell (Upper Bound)", "Mean UMI Count Purity")
if ("GEMs.with..0.Cells" %in% colnames(metrics)) gw0c <- metrics[1, "GEMs.with..0.Cells"] else gw0c <- "NA"
if ("GEMs.with..1.Cell" %in% colnames(metrics)) gw1c <- metrics[1, "GEMs.with..1.Cell"] else gw1c <- "NA"
if ("Fraction.GEMs.with..1.Cell" %in% colnames(metrics)) fgw1c <- metrics[1, "Fraction.GEMs.with..1.Cell"] else fgw1c <- "NA"
if ("Fraction.GEMs.with..1.Cell..Lower.Bound." %in% colnames(metrics)) fgw1clb <- metrics[1, "Fraction.GEMs.with..1.Cell..Lower.Bound."] else fgw1clb <- "NA"
if ("Fraction.GEMs.with..1.Cell..Upper.Bound." %in% colnames(metrics)) fgw1cub <- metrics[1, "Fraction.GEMs.with..1.Cell..Upper.Bound."] else fgw1cub <- "NA"
if ("Mean.UMI.Count.Purity" %in% colnames(metrics)) mucp <- metrics[1, "Mean.UMI.Count.Purity"] else mucp <- "NA"
gem_c2 <- c(as.numeric(gsub(",", "", gw0c)), as.numeric(gsub(",", "", gw1c)), fgw1c, fgw1clb, fgw1cub, mucp)
gem_table <- matrix(c(gem_c1, gem_c2), ncol = 2, byrow = F)
gem_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14)
```

### 3.5 Cell Ranger Report on Cells
```{r echo=FALSE,warning=FALSE}
cell_c1 <- c("Estimated Number of Cells", "Estimated Number of Cell Partitions", "Fraction Reads in Cells", "Mean Reads per Cell", "Median Genes per Cell", "Total Genes Detected", "Median UMI Counts per Cell")
if ("Estimated.Number.of.Cells" %in% colnames(metrics)) enoc <- metrics[1, "Estimated.Number.of.Cells"] else enoc <- "NA"
if ("Estimated.Number.of.Cell.Partitions" %in% colnames(metrics)) {enocp <- metrics[1, "Estimated.Number.of.Cell.Partitions"]} else {cell_tag1 <- paste0(reference, ".", "Estimated.Number.of.Cell.Partitions"); if (cell_tag1 %in% colnames(metrics)) {enocp <- metrics[1, cell_tag1]} else {enocp <- "NA"}}
if ("Fraction.Reads.in.Cells" %in% colnames(metrics)) {fric <- metrics[1, "Fraction.Reads.in.Cells"]} else {cell_tag2 <- paste0(reference, ".", "Fraction.Reads.in.Cells"); if (cell_tag2 %in% colnames(metrics)) {fric <- metrics[1, cell_tag2]} else {fric <- "NA"}}
if ("Mean.Reads.per.Cell" %in% colnames(metrics)) mrpc <- metrics[1, "Mean.Reads.per.Cell"] else mrpc <- "NA"
if ("Median.Genes.per.Cell" %in% colnames(metrics)) {mgpc <- metrics[1, "Median.Genes.per.Cell"]} else {cell_tag3 <- paste0(reference, ".", "Median.Genes.per.Cell"); if (cell_tag3 %in% colnames(metrics)) {mgpc <- metrics[1, cell_tag3]} else {mgpc <- "NA"}}
if ("Total.Genes.Detected" %in% colnames(metrics)) {tgd <- metrics[1, "Total.Genes.Detected"]} else {cell_tag4 <- paste0(reference, ".", "Total.Genes.Detected"); if (cell_tag4 %in% colnames(metrics)) {tgd <- metrics[1, cell_tag4]} else {tgd <- "NA"}}
if ("Median.UMI.Counts.per.Cell" %in% colnames(metrics)) {mucpc <- metrics[1, "Median.UMI.Counts.per.Cell"]} else {cell_tag5 <- paste0(reference, ".", "Median.UMI.Counts.per.Cell"); if (cell_tag5 %in% colnames(metrics)) {mucpc <- metrics[1, cell_tag5]} else {mucpc <- "NA"}}
cell_c2 <- c(as.numeric(gsub(",", "", enoc)), as.numeric(gsub(",", "", enocp)), fric, as.numeric(gsub(",", "", mrpc)), as.numeric(gsub(",", "", mgpc)), as.numeric(gsub(",", "", tgd)), as.numeric(gsub(",", "", mucpc)))
cell_table <- matrix(c(cell_c1, cell_c2), ncol = 2, byrow = F)
cell_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% row_spec(c(1,3,4,5), bold = T, color = "Red")
```

### 3.6 Quality Control Report
```{r echo=FALSE,warning=FALSE}
qc_c1 <- c("Pre-QC Genes", "Post-QC Genes", "Pre-QC Cells", "Post-QC Cells", "% Post-QC Cells","Median of Post-QC Genes per Cell", "Mean of Post-QC Genes per Cell", "Median of Post-QC UMIs per Cell", "Mean of Post-QC UMIs per Cell")
percent_cells <- paste0(round((postqc_cells / preqc_cells * 100), 2), "%")
qc_c2 <- c(preqc_genes, postqc_genes, preqc_cells, postqc_cells, percent_cells, genes_per_cell_median, genes_per_cell_mean, umis_per_cell_median, umis_per_cell_mean)
qc_table <- matrix(c(qc_c1, qc_c2), ncol = 2, byrow = F)
qc_table %>% kable("html") %>% kable_styling(bootstrap_options = "striped", font_size = 14) %>% row_spec(c(2,4,5,6,9), bold = T, color = "Red")
```

```{r echo=FALSE}
# Write the QC summary table for QC report
summary_table <- rbind(sample_table, qc_table, sequencing_table, gem_table, cell_table)
summary_table <- t(summary_table)
summary_table_name <- paste0(outdir, "/3_1_", sample, "_", reference, "_report.csv")
write.table(summary_table, file = summary_table_name, sep = ",", col.names = F, row.names = F, quote = F)

# Write the Meta.data of Seurat Object with nGene/nUMI/p.Mito/ident of each cell
meta_table <- Obj@meta.data
meta_table$cell_id <- row.names(meta_table)
meta_table_out <- meta_table[, c(5,3,1,2,4)]
meta_table_out_file <- paste0(outdir, "/3_2_", sample, "_", reference, "_metadata.txt")
write.table(meta_table_out, file = meta_table_out_file, quote = F, row.names = F, col.names = T, sep = "\t")

# Write the clean count table for subseqent analysis
cleancounts_table <- as.matrix(Obj@data)
newline_c_clean <- colnames(cleancounts_table); newline_r_clean <- rownames(cleancounts_table);
cleancounts_table <- rbind(newline_c_clean, cleancounts_table); row.names(cleancounts_table) <- c("GeneSymbol", newline_r_clean);
cleancounts_table_file = paste0(outdir, "/3_3_", sample, "_", reference, "_counts_clean.txt")
write.table(cleancounts_table, file = cleancounts_table_file, sep = "\t", col.names = F, row.names = T, quote = F)

# Write the raw count table for subseqent analysis
##rawcounts_table <- as.matrix(data)
##newline_c_raw <- colnames(rawcounts_table); newline_r_raw <- rownames(rawcounts_table);
##rawcounts_table <- rbind(newline_c_raw, rawcounts_table); row.names(rawcounts_table) <- c("GeneSymbol", newline_r_raw);
##rawcounts_table_file = paste0(outdir, "/3_4_", sample, "_", reference, "_counts_raw.txt")
##write.table(rawcounts_table, file = rawcounts_table_file, sep = "\t", col.names = F, row.names = T, quote = F)

# Save the working space
obj_name <- paste0(outdir, "/", sample, "_", reference, "_qc.Rdata")
save(Obj, file = obj_name)
```
